### 2013-04-28 MSteenhagen-CV.tex
Some more minor changes and punctuation fixes
Made planned submission date more explicit
Added Utrecht teaching experience to CV

\ind Dissertation on the perceptual nature of pictorial representation\\ Supervisor: Prof. Mark Eli Kalderon

@@

\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ C. philosophy; Philosophy of language

@@

%\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Research \newline presentations}
\medskip
\ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)

@@

% \medskip
% 
% \noindent\href{http://www.hku.nl/web/English.htm}{\emph{Utrecht School of Arts} \vspace{0.01in}}
% 
% \ind 2008-2009. Assistant Lecturer in Art Theory and Cultural History.
% 
% \medskip
% 
% \noindent\href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Dept. Philosophy} \vspace{0.01in}}
% 
% \ind 2007-2008. Teaching Assistant in Aesthetics and Moral Psychology.

@@

\ind Representative, \href{http://www.bppa-online.org}{British Postgraduate Philosophy Association} (UCL, 2011).

>>>>

\ind Dissertation on the perceptual nature of pictorial representation\\ Supervisor: Prof. Mark Eli Kalderon\\Projected submission: Autumn 2014

@@

\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ c. philosophy; Philosophy of language

@@

%\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Research \newline presentations \newline(recent)}
\medskip
\ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)

@@

% \medskip
% 
% \noindent\href{http://www.hku.nl/web/English.htm}{\emph{Utrecht School of Arts} \vspace{0.01in}}
% 
% \ind 2008-2009. Assistant Lecturer in Art Theory and Cultural History.
% \medskip
% 
\ind 2007-2008. Teaching Assistant in Aesthetics. \href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Department of  Philosophy}} \vspace{0.01in}

\ind 2008. Teaching Assistant in Moral Psychology. \href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Department of  Philosophy}} \vspace{0.01in}

\ind 2007. Teaching Assistant in Philosophy of Science. \href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Department of  Philosophy}} \vspace{0.01in}

@@

\ind Representative, \href{http://www.bppa-online.org}{British Postgraduate Philosophy Association} (UCL, 2011)
